\renewcommand{\bibname}{Litteraturliste}
\fancyhead[CE,CO]{}
\fancyfoot[CE,CO]{}
\begin{thebibliography}{2}

\bibitem {lib:DK8000} Timll Technic Inc: \textit{DevKit8000 brugermanual}. \\ 
"Bilag 001 - DevKit8000 User Manual En". 2009.

\bibitem {lib:psoc4_guide} Cypress Semiconductor: \textit{PSoC 4 Pioneer Kit Guide}. \\
"Bilag 002 - CY8CKIT-042 PSoC 4 Pioneer Kit Guide". 2013.

\bibitem {lib:TempHum_DS} Honeywell International Inc.: \textit{Datablad for Temperatur-/Luftfugtighedssensor}. \\
"Bilag 003 - Datablad for Temp og Luftfugtsensor". August 2013.

\bibitem {lib:TempHum_I2C} Honeywell International Inc.: \textit{\IIC Communication with the Honeywell HumidIcon}. \\
"Bilag 004 - I2C Communication with the Honeywell HumidIcon". June 2012.

\bibitem {lib:LightSens} Intersil: \textit{Datablad for lyssensor}. \\
"Bilag 005 - Datablad for lyssensor". Februar 2008.

\bibitem {lib:LM7805_DS} Motorola, Inc.: \textit{Three-Terminal Positive Voltage Regulators}. \\
"Bilag 006 - Datablad for LM7805". Maj 1996.

\bibitem {lib:UHD2_DS} SAIA-Burgess Electronics: \textit{Motor Products}. \\
"Bilag 007 - Motor Products". 2000.

\bibitem {lib:LM75} Maxim: \textit{Digital Temperature Sensor and Thermal
Watchdog with 2-Wire Interface}. \\
"Bilag 008 - Datablad for LM75". 2009.

\bibitem {lib:MSE_06} PRJ3 F15 Gruppe 9: \textit{MSE Øvelse 6}. \\
"Bilag 009 - MSE Øvelse 6". Maj 2015. 

\bibitem {lib:USB20} USB Implementers Forum, Inc.: \textit{USB 2.0 Specification}.\\
\url{http://www.usb.org/developers/docs/usb20_docs/#usb20spec}. Marts 2015.

\bibitem {lib:PSoC_m_git} PRJ3 F15 Gruppe 9: \textit{PSoC Master source code}. \\
\url{https://github.com/PhKP/PSoC_Master}. 2015.

\bibitem {lib:DevKit8000_Addon} Devkit8000 wiki, IHA: \textit{DevKit8000 wiki}. \\
\url{https://redmine.iha.dk/devs/projects/devkit8000/wiki/Addon_board}. Dec 2013.

\bibitem {lib:UART_opensource} Beelen, Teunis van: \textit{RS232 UART-protokol}. \\
\url{http://www.teuniz.net/RS-232/} . Jan 2015.

\bibitem {lib:threadconcept} Codebase.eu: \textit{Multithreading}. \\
\url{http://codebase.eu/tutorial/posix-threads-c/}. Sep 2011

\bibitem {lib:QT} The QT company: \textit{QT info}. \\
\url{http://doc.qt.io/qt-4.8/timers.html}. Feb 2015.

\bibitem {lib:Event_driven_programming} Wikipedia: \textit{Event Driven Programming}. \\
\url{http://en.wikipedia.org/wiki/Event-driven_programming}. Maj 2015.

\bibitem {lib:multi_threading} The Open Group. \textit{Multi threading}. \\
\url{http://pubs.opengroup.org/onlinepubs/9699919799/basedefs/pthread.h.html}. 2013.

\end{thebibliography}